No Title

### 2017-10-26 paper/paper.tex
results from scratch

\begin{figure*}
\centering
\includegraphics[width=0.32\textwidth]{scatter_random_ranked_ca_ratio.pdf}
\includegraphics[width=0.32\textwidth]{scatter_ranked_ca_ratio.pdf}
\includegraphics[width=0.32\textwidth]{scatter_norm_ca_ratio.pdf}
\caption{Same layout as in Figure \ref{fig:scatter_width}. 
This time for the $c/a$ axis ratio. 
The message holds in this case as for the plane width.
The MW is has a significantly low $c/a$ value compared to the
expectation from a spherical distribution and simulations. 
This low value is also $2\sigma$ away from the expactations for an
spherical distribution.
M31 is consistent both with an spherical distribution and the results
from simulations.
However, in this case the axis ratio in the spherically averaged case
is completeley consistent with the expectation from simulations.
\label{fig:scatter_ca_ration}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.32\textwidth]{scatter_random_ranked_ba_ratio.pdf}
\includegraphics[width=0.32\textwidth]{scatter_ranked_ba_ratio.pdf}
\includegraphics[width=0.32\textwidth]{scatter_norm_ba_ratio.pdf}
\caption{Same layout as in Figure \ref{fig:scatter_width}. 
This time for the $b/a$ axis ratio. In this case both the MW and M31
are consistent with the results of a spherical distribution and the
simulations. 
\label{fig:scatter_ba_ration}}
\end{figure*}

@@

\subsection{Satellite distributions in the Local Group}

Figure \ref{fig:lg_scatter} summarizes our main results for the
observed LG satellite distributions.
We see that the \rank\ and \boot\ samples are consistent 
withing the scatter provided by each sample.
We use the median and standard deviation in each sample to define the
most probable value and its associated uncertaintiy.
This allows us to compare the observational values gainst the
distributions derived from the Illustris simulation.

There is a third sample in Figure \ref{fig:lg_scatter}. 
It corresponds to the set of \rand\ points generated
by randomizing the angular positions of the satellites in each pair in
the \boot\ sample. 
This provides a baseline to understand the importance 
of intrinsic satellite's radial profile distribution in driving the
results.

The upper left panel in Figure \ref{fig:lg_scatter} shows that the
planar satellite distributions are located perpendicular to the line
connecting the two galaxies. 
It is remarkable that this alignment is almost perfect for both
satellite distributions. 
The points in the \rand\ simply highlights the expected result for a
random angular distribution is a flat distribution in the range
$0\leq\mu\leq 1$.

The upper right panel shows two interesting things. 
First, the MW satellite plane is thiner than its M31
counterpart. 
This is in principle unexepected since M31 is more
massive than the MW and it should have a broader satellite
distribution. 
The second interesting point is that the MW satellite plane is also
thiner than the spherical randomized expectation, while the M31 plane
is right within the expectation of the randomized satellites. 
This is a another piece of evidence showing the highly structured
satellite distribution in the MW in comparison to M31. 
The fact that the \rand\ samples also show a trend towards thinner MW
planes means that the radial satellite distribution in concentrated in
the MW than it is in M31.

The lower left panel re-inforces the picture of a highly structured
MW. 
It corresponds to the $c/a$ ratio and shows the same trends observed
in for the plane width. 
First, the ratio is lower for the MW than it is for M31; second, the
ratio for the MW is also lower than the expectation for the randomized
sample while the results for M31 is within the expectations from \rand.  
In this case the median value of the \rand\ distributions follow the
$1:1$ line as expected.
The lower right panel does not show any surprises. 
All the distributions from \rank, \boot\ and \rand\ are consistent
both for the MW and M31.

We can quantify the degree at which the observed satellite distributions are 
different from their spherically randomized counterparts.
Figure \ref{fig:lg_distribution} shows the probability distributions
from the \rand\ pairs with an overplot of the LG values.
The upper left panel shows the power law distribution for $\mu$. The
results are not perfectly horizontal because the optimal power value
$\hat{alpha}$ is slightly different from $1$, the uncertainties in
this value are naturally consistent with the unit value expected for
an homogeneous distribution. 
In this case all values are equiprobable.
In the case of the $b/a$ ratio (lower right panel) both the MW and M31
are consistent with the average values expected from \rand\ distribution.
Remarkably, the plane width and $c/a$ ratio for the MW are significantly 
different from the \rand\ expected values, while the M31 values are
sistematically within the expectations.

The comparison of the observed satellite distribution against its onw
version, but spherically randomized, tells us that the MW satellite
planar structure is remarkably different from a random distribution,
while for the M31 distribution there isn't a significant difference
from the random expectation.

>>>>

\begin{figure*}
\centering
\includegraphics[width=0.32\textwidth]{scatter_random_ranked_ca_ratio.pdf}
\includegraphics[width=0.32\textwidth]{scatter_ranked_ca_ratio.pdf}
\includegraphics[width=0.32\textwidth]{scatter_norm_ca_ratio.pdf}
\caption{Same layout as in Figure \ref{fig:scatter_width}. 
This time for the $c/a$ axis ratio. 
The message holds in this case as for the plane width.
The MW is has a significantly low $c/a$ value compared to the
expectation from a spherical distribution and simulations. 
This low value is also $2\sigma$ away from the expactations for an
spherical distribution.
M31 is consistent both with an spherical distribution and the results
from simulations.
However, in this case the axis ratio in the spherically averaged case
is completeley consistent with the expectation from simulations.
\label{fig:scatter_ca_ratio}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.32\textwidth]{scatter_random_ranked_ba_ratio.pdf}
\includegraphics[width=0.32\textwidth]{scatter_ranked_ba_ratio.pdf}
\includegraphics[width=0.32\textwidth]{scatter_norm_ba_ratio.pdf}
\caption{Same layout as in Figure \ref{fig:scatter_width}. 
This time for the $b/a$ axis ratio. In this case both the MW and M31
are consistent with the results of a spherical distribution and the
simulations. 
\label{fig:scatter_ba_ratio}}
\end{figure*}

@@

\subsection{Plane Width}

Figure \ref{fig:scatter_width} summarizes the main results for the plane
width distributions.
The panel on the left compares the results for the MW and M31
observations against its randomized version. 
The most interesting outcome is that the MW plane width is smaller
than $95\%$ of the planes computed from the randomized distribution,
while the M31 plane width is consistent with the same distribution.
